The expected shape of the Milky Way's Dark Matter halo

### 2018-10-12 Paper/paper.tex
edit

\section{Numerical Simulations}
In this work we use the results of the state-of-the art Auriga
simulations \cite{auriga}. It selected a set of 30 isolated halos from
the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
project \cite{Eagle}. Each halo was identified with the algorithm
"Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively
links particles if they are closer than some threshold distance
referred as linking length. EAGLE follows the evolution of fixed-mass
particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from
$z=127$ to $z=0$, adopting the $\Lambda$CDM model from the
\cite[Planck Collaboration et al. (2014)]{Planck_Collaboration_2014},
which is characterized by $\Omega_\Lambda=0.693$,
$\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \&
$\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.

These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ varied between
$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
  is defined as the mass enclosed within the virial radius $R_{200}$
  at which the density becomes 200 times the critical density of the
  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
with the (AREPOOO HERE) by increasing the mass resolution of the
particles belonging to them and diminishing the resolution of the rest
of the particles.

Various versions of each halo were modelled with different degrees of
realism. All 30 halos were simulated within a level-4-degree of
resolution defined for Aquarius simulations corresponding to $\tilde
3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
M_\odot$. The principal details of each of these halos are consigned
on the table \ref{tab:level4}. From these halos, 6 of them where
re-simulated at level 3 (higher) resolution taking into account a
spatial factor of 2 in each dimension. For more information about
level 3 halos, their details are printed on table
\ref{tab:level3}. Furthermore, fore each halo in each level of
resolution there are two versions of the simulation. One of tracks the
evolution of DM-only particles while the remaining one evolves DM and
baryions with magneto-hydrodynamical (MHD) physics, including DM.

>>>>

In this work we use the results of the state-of-the art Auriga
simulations \cite{auriga}. 
The objects in those simulations were selected from a set of 30 isolated halos in
the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
project \cite{Eagle}. 
These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ varied between
$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. 
These halos were re-simulated with higher resolution an varying
physical realism using the AREPO code \citep{codee}.

All 30 halos were simulated within resolution defined for Aquarius
simulations corresponding to $\sim 3\time 10^6$ high resolution particles of $\sim 2.5 \time 10^5
M_\odot$.  
This resolution is labeled as Level 4, the main details for each halo
are consigned in Table \ref{tab:level4}. 
From these 30 halos, 6 of them where re-simulated at higher resolution
(labeled as Level 3) taking into account a spatial factor of 2 in each
dimension.   
Details of Level 3 halos are in Table \ref{tab:level3}. 
Furthermore, fore each halo in each level of
resolution there are two versions of the simulation. One of tracks the
evolution of DM-only particles while the remaining one evolves DM and
baryions with magneto-hydrodynamical (MHD) physics, including DM.
